---
title: "JUMIA R WEB SCRAPER"
author: "SHADRACK YEGON"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---


### Functions Used
* read_html()-creates html document from a url/link
* html_nodes()-selects part of a document using css selectors
* html text()-extract text from selected nodes
* html_table()-extract table from selected nodes
* View()-Used for printing the table

### Data Source:
Click [here](https://www.jumia.co.ke/catalog/?q=sumsung+smartphones&page=1#catalog-listing) to open jumia website

### Load the  libraries
```{r,message=FALSE}
library(tidyverse)
library(rvest)
library(gtExtras)

```
## 1.Webscraping Name and Price of the first 10(out of 40) Different sumsung smartphones from a page 
```{r}
link=("https://www.jumia.co.ke/catalog/?q=sumsung+smartphones&page=1#catalog-listing")
  page=read_html(link)
  Name<-page %>% html_nodes(".info .name") %>% html_text()
  Price<-page %>% html_nodes(".info .prc") %>% html_text()
  df<-data.frame(Name,Price) %>% head(10)
  df %>% gt() %>% tab_header(title="Sumsung Smartphones") %>% 
    cols_align("left")
  

```



## 2.Web scarping the first 50(out of 200) rows from multiple pages(1-5)
```{r}
df=data.frame()
for (page_no in c(1:5)){
  link=paste0("https://www.jumia.co.ke/catalog/?q=sumsung+smartphones&page=",page_no,"#catalog-listing")
  page=read_html(link)
  Name<-page %>% html_nodes(".info .name") %>% html_text()
  Price<-page %>% html_nodes(".info .prc") %>% html_text() 
  page_no=print(paste("page",page_no))
  df=rbind(df,data.frame(Name,Price)) %>% head(50)
  
}
df %>% gt() %>% tab_header(title="Sumsung Smartphones") %>% 
    cols_align("left")

```



## 3.Separating the "Name" column into 4 columns
```{r warning=FALSE}
df=data.frame()
for (page_no in c(1:5)){
  link=paste0("https://www.jumia.co.ke/catalog/?q=sumsung+smartphones&page=",page_no,"#catalog-listing")
  page=read_html(link)
  Name<-page %>% html_nodes(".info .name") %>% html_text()
  Price<-page %>% html_nodes(".info .prc") %>% html_text() 
  page_no=print(paste("page",page_no))
  df=rbind(df,data.frame(Name,Price)) %>% head(50)
  
}
df %>% separate(Name,c("Model","Inches","Storage_capacity","Battery"),
                sep=",") %>%
  gt() %>% tab_header(title="Sumsung Smartphones") %>% 
    cols_align("left")

 
```


