---
title: "Regression Analysis in R"
author: "Yegon Shadrack"
date: "2024-09-04"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1.Simple linear regression 

### Load the data
```{r }
library(tidyverse)
library(ggplot2)
```

### Load the data
The data comes from car dataset showing the car speed  and the stopping distance(dist)
```{r}
cars %>% head(5)
```

### Create the Model
```{r}
cars %>% lm(dist~speed,data=.) %>% summary()
```

### Findings
1. P-value associated with F-statistics is very small showing that at least one of the predictor variable is significant predictor of Outcome variable.

2. R-squared=0.65,Indicates that 65% of the change in stopping distance can be explained by explained by the change in speed.
 
### conclusion 
 model: dist=-17.58+3.93(speed)
Increasing the speed of the car by 1 unit increases the car stopping distance by 3.93 ft


## 2.Multiple linear regression

### Load the data
The data is from Trees dataset and it shows the  Diameter(girth), Height and Volume for Black Cherry Trees.
I wanted to investigate whether there is any relationship between Volume,diameter(girth)  and height.
```{r}
trees %>% head(5)
```

### Create the Model
```{r}
trees %>% lm(Volume~Girth+Height,data=.) %>% summary()
```
### Findings
1. P-value associated with F-statistics is less than 0.5,showing that at least one of the predictor variable is significant.

2. Individual p-values of the coefficients are all significant indicating that height and girth is significant predictor of volume.

3. Adjusted R-squared=0.94,showing that 94% of the change in volume can be explained by both the change in  girth and height.

### Conclusions
model: Volume=-57.99+4.71(Girth)+0.34(Height)

* keeping other factors constant,1 inch increase in Girth results in 4.71 cubic ft increase in volume
* Also ,keeping girth constant,a one unit increase in height ,increases the volume by 0.33 cubic ft






